#Cleaning Bad Data with R - 2 - Missing Rows
#Rushikesh Maheshwari
#resource Link: https://www.linkedin.com/learning/cleaning-bad-data-in-r/missing-values?u=2343682

#Loading the tidyverse directory
```{r}
library(tidyverse)
```


#Setting the directory and Importing Data
```{r}
setwd("C:/Users/Admin/Documents/Bad-Data-Handling-in-R")

d <- read_csv("publiclands.csv")
head(d)
```

#Checking the row numbers in the data set!
```{r}
# How many rows are there?
nrow(d)
unique(d$State)
```
#So we have about 8 states and thier corresponding values missing. So lets create another table below

```{r}
# Insert missing states
states <- tibble(State=c('Connecticut', 'Delaware', 'Hawaii', 'Iowa', 'Maryland', 
                                 'Massachusetts','New Jersey', 'Rhode Island'), 
                         PublicLandAcres=c(0,0,0,0,0,0,0,0))
```
#Now lets combine these two tables by rows using rbind command
```{r}
d <- rbind(d,states)
view(d)
```
#Now lets sort this data by state names
```{r}
d <- d[order(d$State),]
view(d)
```
#Now we have the data sorted by state name with corresponding Public Land acre values
